\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-04-18 archive.tex
better deep programming montage

\begin{figure}
  \includegraphics[width = \textwidth]{figures/dpl/montage.pdf}
  \caption{Top: Learned libraries diagrammed as networks. Arrows point from a learned concept to all other concepts that use it. Bottom: Deeper networks solve more testing tasks, both as measured by average depth (left) and maximum depth (right). Full model (circles on scatterplots) learns deeper libraries than no-recognition-model ablation (crosses on scatterplots). Each scatter plot point run with a different random seed.}\label{depthMontage}
  \end{figure}

>>>>

\begin{figure}
  \includegraphics[width = \textwidth]{deepMontage.pdf}
  \caption{Top: Learned libraries diagrammed as networks. Arrows point from a learned concept to all other concepts that use it. Bottom: Deeper networks solve more testing tasks, both as measured by average depth (left) and maximum depth (middle), while total library size is more weakly associated with solving tasks (right). Full model (circles on scatterplots) learns deeper libraries than no-recognition-model ablation (crosses on scatterplots). Each scatter plot point run with a different random seed.}\label{depthMontage}
  \end{figure}
